---
title: "Repr. research assignment 1"
author: "Aurel Prosz"
date: '2017 október 28 '
output: html_document
---
## System Information
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
Sys.info()

```
## analyze_data.R
### Loading and preprocessing the data
First we read in the raw data from the specific file "activity.csv".  
**Don't forget to set your working directory where this file presents!**  
```{r}
datax <- read.csv("activity.csv", sep = ",", 
     na.strings = "NA")


```
Let's look at the first 5 rows of this data:
```{r}
head(datax, 5)

```
We should format the *date* column to Date format:
```{r}
class(datax$date)
datax$date <- as.Date(datax$date)
class(datax$date)

```
### What is mean total number of steps taken per day?

Aggregate the data frame by *date* column:
```{r}
datax.sums <-  aggregate(x = datax["steps"],
     FUN = sum,
     by = list(Group.date = datax$date), 
     na.rm=TRUE)

head(datax.sums, 5)
```
Make a histogram from the results:

```{r, fig.width=6, fig.height=6}
hist(datax.sums$steps, col = "red", 
     xlab = "Total number of steps", 
     breaks = 20, 
     main = "Histogram of total number of steps per day")
```

Calculate the median and the mean for the total number of steps per day:
```{r}
numberofsteps.median <- median(datax.sums$steps)
numberofsteps.mean <- mean(datax.sums$steps)

```
The **median** is `r numberofsteps.median` and the **mean** is `r numberofsteps.mean`

